\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{enumerate}
\usepackage{tikz}
\usepackage{hyperref}
\usepackage{listings}
\usetikzlibrary{shapes.geometric, arrows}
\setlength{\tabcolsep}{18pt}
\usepackage{hyperref}
\usepackage{rotating}
\usepackage{multirow}
\hypersetup{
    colorlinks = true,
    linkbordercolor = {white},
    linkcolor = {red},
}
\usepackage{geometry}
\geometry{
    a4paper,
    % total={170mm,257mm},
    left=16mm,
    top=3mm,
}

\title{Assignment 2}
\author{Gohil Dwijesh \\ 2017CS50407
        \and Prafful \\ 2017CS10369}
\date{September 2019}
    
\begin{document}
\maketitle
%-----------------------------------------------------------------------
\section{Extensions}
    \subsection{User may disconnect arbitrarily by pressing Ctrl-C. How will you deal with such a scenario?}
    The user can unregister by either sending a  message to unregister or by pressing Ctrl-C. If the client application is closed (Ctrl-C), then exception occurs whenever socket is accessed in the server thread corresponding to the client. This exception is caught and the user is unregistered and then the thread is closed.
    \subsection{How would you extend the client applications to deal with offline users?}
    We can maintain a hash table. Hash table will be indexed with user id and each of its entry will contain list of pending messages to that user id. Let us say $user_{1}$ wants to send message to $user_{2}$. $user_{2}$ is offline. So the server can insert the message in the hash table(using $user_{2}$ as index). Now after some time $user_{2}$ becomes online. $user_{2}$ will first send TOSEND and TORECV message to the server. On receiving these packets server will check if there is any list of pending messages for $user_{2}$ entry in hash table or not. If there is then the server will send the messages to $user_{2}$. This is how we can extend our client application to deal with offline users.
\section{Cases Handled}
\begin{enumerate}
    \item User can send \textbf{multiple lines} in one go.
    \item \textbf{User already registered:} Let us say $user_{1}$ is online. If any other client will try to register with same user id $user_{1}$ then server will reject the connection request and will close all the sockets. User will be notified with a message that user id already registered, use other user id.
    \item \textbf{Partial socket closing:} Let us say $\alpha$ wants to send packet to $\beta$. $\alpha$ will send SEND packet to Server. Server finds that there is no issue with header. Server sends FORWARD packet to $\beta$. Now $\beta$ finds that header is incomplete. This implies that there is something wrong with $\beta$\'s format checker for FORWARD packet. So any FORWARD packet it is going to receive, will fail to parse. \textbf{So the server will close the receive socket but server will
    keep send socket open for $\beta$. Now $\beta$ can send the packets but can not receive the packets.}
    \item \textbf{Ctrl-C:} The user is unregistered even when client program is closed abruptly(Ctrl-C). 
\end{enumerate}{}
%-----------------------------------------------------------------------
\end{document}
